Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-03-28 tex/introduction/machine_learning.tex
some citations

The \emph{receiver operating characteristic} (ROC) curve for binary classifiers plots the true positive rate against the false positive rate for all thresholds between $0$ and $1$.
The plot indicates the correctness of the model \wrt its confidence.
The ROC curve for a perfect model ($100\%$ accuracy) would follow the left vertical axis and the top horizontal axis.
The area under the ROC curve (\emph{AUC}) is a commonly used measure for model quality. \todo{cite paper???}

@@

One popular Ensemble Model is the Random Forest, which combines several Decision Trees trained on random sub-samples of the training data.
This overcomes the tendency of Decision Trees to over-fit on their training data.
Another advantage of Random Forests is that they typically produce good results on only few training instances already.

>>>>

The \emph{receiver operating characteristic} (ROC) curve for binary classifiers plots the true positive rate against the false positive rate for all thresholds between $0$ and $1$.
The plot indicates the correctness of the model \wrt its confidence.
The ROC curve for a perfect model ($100\%$ accuracy) would follow the left vertical axis and the top horizontal axis.
The area under the ROC curve (\emph{AUC}) is a commonly used measure for model quality \cite{bradley19971145}.

@@

One popular Ensemble Model is the Random Forest~\cite{Breiman:2001:RF:570181.570182}, which combines several Decision Trees trained on random sub-samples of the training data.
This overcomes the tendency of Decision Trees to over-fit on their training data.
Another advantage of Random Forests is that they typically produce good results on only few training instances already.
